Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-04-11 ms.tex
more edits

\begin{abstract}
\noindent
The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state. As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observables of clusters can lead to accurate estimates of their total masses. Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion. We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will observe many hundreds of square degrees. HETDEX will employ the new VIRUS instrument, an integral field unit (IFU), covering the blue/optical portion of the spectrum (3500--5500~\AAA) blindly in two fields for a total of 420 \degsq\ on the sky with fibers with a 1/4.5 fill factor. This allows surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$). We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field. For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits. We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities. Using both observing strategies, we produce cluster mass probability density functions $P(M_{200}|\vec{x})$ of a cluster mass ($M_{200}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$. \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations}.
\end{abstract}

@@

\editorial{The wording here needs to be updated when we settle on the verbage for everything else.} This work plans to address these concerns in the following ways. We use simulated observations which target individual galaxy clusters to investigate the recovery of parameters with such observations. Secondly, we create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass. Each observation strategy will further be constrained with ``ideal'' and ``realistic'' knowledge. Ideal knowledge assumes that we know which individual galaxy is assigned to which cluster. With realistic knowledge this is unknown and must be determined prior to the estimation of the cluster properties. Both of these strategies will better allow future work to predict the number and types of galaxy clusters which should be observed with VIRUS during both the HETDEX survey portion and through targeted follow up observations.

@@

The Buzzard mock galaxy catalogs (R. Wechsler et al., private communication) cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses.

@@

We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}. We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compare it galaxies in a redshift window of $\Delta z\pm0.01$. We find a very good agreement between the predicted HMF and the observed distribution of clusters. \editorial{Could show a figure comparing the Buzzard catalog to a plot of the HMF for a couple of redshifts. Might be helpful, might not matter.}

@@

The left panel of Figure~\ref{fig: oii sdss} shows the CMD of all SDSS galaxies. Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by the two colored boxes. The histograms show in the Figure's right panel show the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin around the individual catalog galaxies. We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux. \editorial{We could add a plot like the corner plot to show the multi-dimensionality of this process.}

@@

Each mask is created to reproduce the HETDEX IFU pattern, see Figure~\ref{fig: ifu layout}. The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}. The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky.

The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing. This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}. Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next. To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65 slightly decreased from the expected filling factor of 1/4.5.

@@

\subsection{Cluster Redshift}
The accurate determination of the cluster redshift ($z_c$) is crucial to the reliability of all following measurements. An incorrect cluster redshift introduces errors into the measured line-of-sight velocity (LOSV) and corresponding dispersion, which, in turn, contributes to errors associated with dynamical mass and radius.

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster. However, because the standard mean can be quite sensitive to outliers or otherwise contaminated data, we require a more resistant statistic, and turn to the biweight location estimator \citep{Beers1990} which provides improved performance.

@@

The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
\end{equation}
where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively. Using a Monte Carlo Markov Chain (MCMC) sampler ({\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

@@

We begin with the perfect knowledge observations. These observations are of the same clusters as the targeted observations but without any observational limits. The cluster masses predicted by Equation \ref{eq:power law} gives the following results. Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.002}$ dex. The scatter in recovered masses can be attributed to both physical and numerical effects. The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which increases the observed LOSVD increasing the predicted mass \citeeg{Ntampaka2015}. Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects. The cluster masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership. In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.

@@

For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.003}$ dex and $\mu_{bias} =0.11\pm{0.009}$ dex, respectively. So for the clusters that we detect with survey observations, we obtain similar levels of accuracy as to the targeted observations, on the average. This does not mean that the survey observations cannot be improved by targeted observations. In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD PDF. The targeted observations performs similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.

@@

\editorial{Maybe a sentence or two that specifically say we don't think this is a problem.}

@@

		\rottext{4}{ML Based} & Power Law & \nd & $1.41\pm{inf}$ & $0.40\pm{0.05}$ & $0.41\pm{0.02}$ & $0.38\pm{0.01}$ & $0.32\pm{0.01}$ & $0.25\pm{0.02}$ & $0.15\pm{0.06}$ \\
		&$\sigma$ & \nd & $0.30\pm{inf}$ & $0.27\pm{0.03}$ & $0.28\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.02}$ & $0.29\pm{0.11}$ \\
		&$\sigma, z$ & \nd & $0.61\pm{inf}$ & $0.22\pm{0.03}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.02}$ & $0.30\pm{0.11}$ \\
		&$\sigma, z, N_{gal}$ & \nd & $0.80\pm{inf}$ & $0.19\pm{0.02}$ & $0.21\pm{0.01}$ & $0.20\pm{0.01}$ & $0.19\pm{0.01}$ & $0.19\pm{0.01}$ & $0.23\pm{0.08}$ \\

@@

% \editorial{This is a place holder section. One of the things missing to bring this work full circle is a discussion about how the uncertainties in cluster masses impact the derived cosmological parameters. I am currently doing a literature review looking for references that discuss how the mass errors impact the derived parameters. Here we want to be able to say ``so and so show that errors on clusters masses need to be better than blah to recover $\sigma_8$ and $\Omega_m$ to better than blah, which is useful for blah. We show that with XXXX kind of data spectroscopic surveys like HETDEX can achieve this but only with YYYY kind of data quality.'' If it isn't going to do that well, then how much constraint could HETDEX/HETDEX-like surveys put on cosmological parameters? How good would they have to get to test gravity? (or the dark energy equation of state)}

@@

For a survey such as HETDEX, we can estimate the constraints on $\sigma_8h^{-1}$ using Equation \ref{eq:sigElapprox}. Considering clusters with masses above $10^{14}$ \Msol, with perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty is reduced to $\sim 0.075$ dex or about 20\%. This gives a uncertainty on $\sigma_8h^{-1}$ of 7\%. For clusters above $10^{14}$ \Msol, survey observations can constrain the masses to about 51\% which, in turn, constrains $\sigma_8h^{-1}$ to 20\%.

Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ to better precision than other methods (\eg, CMB, WL, X-ray) seems bleak. For the $\sim1500$ clusters detected with survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%. For a fully targeted survey, about 14000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.    
\editorial{Here I want to say a word or two about how all hope isn't lost. We can still use HETDEX to reduce the scatter on the richness-mass relationship which can help other estimators get down to the levels we need to really nail down these numbers.}

@@

\section*{Acknowledgements}
The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work. We also thank Steven W. Crawford for many helpful discussions. This research made use of This research made use of the {\tt IPython} package \citep{Perez2007} and {\tt matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}. Figure \ref{fig: probability corner} is heavily based on \cite{Foreman-Mackey2016}. Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/. The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.

>>>>

\begin{abstract}
\noindent
The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state. As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observables of clusters can lead to accurate estimates of their total masses. Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion. We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ the new VIRUS integral field unit (IFU) spectrograph, over 420 \degsq\ on the sky with a 1/4.5 fill factor. The instrument covers the blue/optical portion of the spectrum (3500--5500~\AAA), allowing surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$). We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field. For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits. We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities. Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$. \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations}.
\end{abstract}

@@

This work plans to address these concerns in the following ways. We create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass. We compare these results to a series of targeted galaxy cluster observations, where each member galaxy is assumed to be observed. Each of these observations use realistic uncertainties from galaxy magnitude and line-flux limits. These strategies will better allow future work to predict the number and types of galaxy clusters which should be observed with VIRUS during both the HETDEX survey portion and through targeted follow up observations.

@@

The Buzzard mock galaxy catalogs (R. Wechsler et al., private communication) cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\sc 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\sc LGadget-2} (a version of {\sc Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\sc ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses.

@@

We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}. We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\sc HMFcalc} \citep{Murray2013} and compare it galaxies in a redshift window of $\Delta z\pm0.01$. We find a very good agreement between the predicted HMF and the observed distribution of clusters.

@@

The left panel of Figure~\ref{fig: oii sdss} shows the CMD of all SDSS galaxies. Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by the two colored boxes. The histograms show in the Figure's right panel show the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin around the individual catalog galaxies. We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.

@@

The HETDEX IFU pattern is illustrated in Figure~\ref{fig: ifu layout.} The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}. The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky. The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.

This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}. Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next. To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65 slightly decreased from the expected filling factor of 1/4.5.

@@

\subsection{Cluster Redshift}
The accurate determination of the cluster redshift ($z_c$) is crucial to the reliability of all following measurements. An incorrect cluster redshift introduces error into the measured line-of-sight velocity (LOSV) and corresponding dispersion, which, in turn, contributes to errors associated with dynamical mass and radius.

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster. For this work we rely on the biweight location estimator \citep{Beers1990} because it is resistant to outlying galaxies. Although this work assumes that we know each galaxy's redshift to infinite precision, in practice, we find a simple weighted mean provides a reliable estimate of $z_c$ when there are uncertainties on the individual galaxy redshifts.

@@

The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
\end{equation}
where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively. Using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

@@

We begin with the perfect knowledge observations. These observations are of the same clusters as the targeted observations but without any observational limits. The cluster masses predicted by Equation \ref{eq:power law} gives the following results. Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.002}$ dex and $\sigma_{bias} = 0.24\pm{0.001}$. The scatter in recovered masses can be attributed to both physical and numerical effects. The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which increases the observed LOSVD increasing the predicted mass \citeeg{Ntampaka2015}. Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects. The cluster masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership. In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.

@@

For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.003}$ dex, $\sigma_{bias} = 0.37\pm{0.002}$ and $\mu_{bias} =0.11\pm{0.009}$ dex, $\sigma_{bias} = 0.36\pm{0.006}$ , respectively. So for the clusters that we detect with survey observations, we obtain similar levels of accuracy as to the targeted observations, on the average. This does not mean that the survey observations cannot be improved by targeted observations. In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD PDF. The targeted observations performs similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.

@@

Based on these tests, we do not find a significant cause for concern with using trained ML methods to predict our galaxy cluster masses when the underlying cosmological choices are different. This highlights the versatility of our chosen ML method. The ML method could be further diversified by including cluster measurements from a wide range of cosmological simulations (or observations) which, in affect, marginalizes over all the cosmological assumptions further reducing the dependence.

Based on these tests, we do not find a significant cause for concern about training our ML methods using simulations which may have a different cosmology than the target observations. We

@@

		\rottext{4}{ML Based} & Power Law & \nd & $1.41\pm{...}$ & $0.40\pm{0.05}$ & $0.41\pm{0.02}$ & $0.38\pm{0.01}$ & $0.32\pm{0.01}$ & $0.25\pm{0.02}$ & $0.15\pm{0.06}$ \\
		&$\sigma$ & \nd & $0.30\pm{...}$ & $0.27\pm{0.03}$ & $0.28\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.02}$ & $0.29\pm{0.11}$ \\
		&$\sigma, z$ & \nd & $0.61\pm{...}$ & $0.22\pm{0.03}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.02}$ & $0.30\pm{0.11}$ \\
		&$\sigma, z, N_{gal}$ & \nd & $0.80\pm{...}$ & $0.19\pm{0.02}$ & $0.21\pm{0.01}$ & $0.20\pm{0.01}$ & $0.19\pm{0.01}$ & $0.19\pm{0.01}$ & $0.23\pm{0.08}$ \\

@@

@@

For a survey such as HETDEX, we can estimate the constraints on $\sigma_8h^{-1}$ using Equation \ref{eq:sigElapprox}. Considering clusters with masses above $10^{14}$ \Msol, with perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is reduced to $\sim 0.075$ dex or about 20\%. This gives a uncertainty on $\sigma_8h^{-1}$ of 7\%. For clusters above $10^{14}$ \Msol, survey observations can constrain the masses to about 51\% which, in turn, constrains $\sigma_8h^{-1}$ to 20\%.

Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ to better precision than other methods (\eg, CMB, WL, X-ray) seems bleak. For example \cite{deHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey. For the $\sim1500$ clusters detected with survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%. For a fully targeted survey, about 14000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.

@@

\section*{Acknowledgements}
The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work. We also thank Steven W. Crawford for many helpful discussions. This research made use of This research made use of the {\sc IPython} package \citep{Perez2007} and {\sc matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}. Figure \ref{fig: probability corner} is heavily based on \cite{Foreman-Mackey2016}. Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/. The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
